Testing the precision of Bangla Communication Scale: Item Response Theory Guided Analysis

### 2022-02-04 manuscript.Rmd
Title changed

---
title             : "Psychometric Evaluation of the Bangla Communication Scale through Classical Test Theory and Item Response Theory"
shorttitle        : "Bangla Communication Scale"

>>>>

---
title             : "Psychometric Evaluation of the Bangla Communication Scale Among Adolescents:Latent structure, Reliability, validity, and gender invariance in a Bangladeshi adolescent sample"
shorttitle        : "Bangla Communication Scale"
